Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-24 krs-survey.tex
Spell checking

Those questions have in common one prerequisite to be answered: the robot must
be able to manipulate \emph{explicitely} knowledge, and hence, need a wayto
represent the knowledge.

@@

We have classified the features of knowledge representation systems (KRS) into
six broad categories: \emph{what can be represented?} or the
\emph{expresiveness} question ; \emph{how things are represented?} ; \emph{what
reasoning techniques are offered?} ; \emph{how knowledge is acquired and
anchored?} ; \emph{how the knowledge is made available and used by the other
components of the robot?} and \emph{which actual knowledge is stored?} or the
\emph{knowledge instanciation} question.

We have identified over ten projects that are either explicitely advertised as
knowledge representation systems or involve explicit knowledge manipulation
within a robot. By knowledge manipulation, we mean symbolic representation of
assertions, be it static statements on the world or spatio-temporal events, and
reasoning on this representation. Proeminent features of each of these systems
illustrate how the various features of a knowledge representation system are
currently implemented.

@@

Every robotic system has, implicitely or not, some knowledge representation
systems. It may range from a simple state vector to an explicit symbolic
knowledge base.  This survey focuses on the right end of this spectrum:
symbolic systems, suited for abstract reasoning.

@@

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarly designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are able of on-line, dynamic knowledge acquisition and reasoning 
    (\ie not a simple static database).
\end{inparaenum}

@@

While classical cognitive architectures like {\sc Soar} or {\sc ACT-R} have
declarative knowledge modules~\cite{Derbinsky2010} and have been recently used
on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for instance), they are
also absent from this survey because we did not find much references in the
litterature on knowledge manipulation and representation applied to robotic
scenarii in these architectures.

@@

In a slightly broader context, Heintz et al.~\cite{Heintz2008} define
\emph{knowledge processing middlewares} as systems supporting ``declarative
specifications for flexible configuration and dynamic reconfiguration of
context dependent processing at many different levels of abstraction''. They
identify six characteristics: the system must be able to merge informations
from different, possibly distributed sources; it should support quantitative as
well as qualitative processing of information, it should offer bottom-up and
top-down processing, it should be able to deal with uncertainty, allow for
``flexible configuration and reconfiguration'' (which require what we call
\emph{non-monotonicity} in this article) and eventually Heintz et al. call for
meta-knowledge and introspective capacities (``declarative specification of the
processing functionalities''). In this paper, we focus our analysis on similar
system with however an emphazise on the symbolic capabilities.

Several surveys compare global cognitive architectures (\cite{Vernon2007, Chong2009}).
Vernon et al.~\cite{Vernon2007} split these architectures into two broad
categories: the \emph{cognitivist} ones (where cognition is considered as an
explicit computation problem, often based on symbol manipulation), and the
\emph{emergent} ones (where cognition only exists as a result of the
interaction of the system with its environment). The approaches presented in
this paper are, at a few exceptions, prototypical \emph{cognitivist} approaches
that aim at making knowledge explicit within the robot architecture. Vernon et
al. propose twelve \emph{characteristics of cognitive system} to compare
architectures. Amongst them, they mention the \emph{inter-agent epistemology} (how
the structure of the world is captured in a representation and shared), the
relation to \emph{embodiement}, the ability to \emph{anticipate} and to
\emph{adapt}, and the mechanisms of \emph{motivation}. While presented at the
level of the whole robotic architecture, these features also translate into
knowledge representation strategies and are relevant to our study.

@@

Section~\ref{sect|surveyed-systems} then presents each of the systems we
examinated, and underlines their specificities.

@@

A related ability is called \emph{pre-supposition accomodation}: if one of the
agent moves behind another one, with the brownie dough in its arm, and says
``be careful, I'm behind you!'', we want the first agent to be able to
represent both symbolically and geometrically (because, for instance, if the
agent want to move, it must take into account the new obstacle) something that
was not directly perceived. A knowledge representation system may be able to
provide structures to represent and reason about such cases.

@@

Note that most of these logic formalisms are still active research field by
their own, and practical considerations (especially the availability of
reasoners performant enough for on-line use on a robot) often constraint the
choice of a logical formalism and a level of expressive power.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{expressive_overlap_dl_horn.pdf}
    \caption{Expresiveness overlap of Description Logics and logic programs
    based on Horn clauses, taken from~\cite{Grosof2003}}
    \label{fig|overlap_dl_horn}
\end{figure}

Figure~\ref{fig|overlap_dl_horn} shows that the expresive power of description
logics and Horn clauses partially overlaps. In section~\ref{sect|reasoning} we
mention extensions to description logics based on rule systems to bring closer
the two approaches.

The relationships between expressive power and reasoning complexity that follow
has been extensively studied for Description Logics.
Zolin~\cite{ZolinDLComplexityNavigator} maintains a ``complexity navigator''
that allows to conveniently explore these relationships and indexes most of the
litterature on that subject.

@@

Introspection must be distinguished from meta-cognition: While introspection
may require meta-cognition (for instance to be able to expose its internal
knowledge), it is not always mandatory. The current state of the robot can be
represented as a simple instanciation of a specific category (for instance, if
the robot give an object to the human, this state could be represented with the
triplets \setstmt{robot performs action1, action1 isA Give}.

@@

A particularly important aspect of introspection relates to the description of
its own capabilities: which sensors/actuators/computation services exist and
are currently available ?  While at a first level, these descriptions can be
static (\eg the robot has one laser scanner and two arms), at a second level,
the description is updated and reflect the current (and possibly past and
future) state of the robot. Note that these description may also invlove
geometric descriptions (a kinematic chain, the pose of a device, etc.) that may
be deported outside of the main knowledge base. Efforts trying to formalize,
maintain and expose the capabilities and state of a robot are not new (and
ground themselves in work and techniques for self-descriptive remote procedure
calls in computing science), but take a renewed importance with applications
for high-level multi-robot cooperation. Recent work in that direction
include~\cite{Kunze2011}.

@@

Memory has been studied at lenght in the cognitive psychology and
neuropsychology communities: Atkinson and Shiffrin~\cite{Atkinson1968}
introduce the idea of \emph{short-term} and \emph{long-term} memory,
Anderson~\cite{Anderson1976} splits memory into \emph{declarative} (explicit)
and \emph{procedural} (implicit) memories, Tulving~\cite{Tulving1985} organizes
the concepts of \emph{procedural}, \emph{semantic} and \emph{episodic} memories
into a hierarchy. Short-term memory is refined with the concept of
\emph{working memory} by Baddeley~\cite{Baddeley2010}
(Figure~\ref{fig|memory_models}).

@@

Most knowledge representation systems offers some kind of memory as a pool of
facts that are not forgotten by the robot until it is halted (this memory is
often refered as a \emph{working memory}, but with a meaning unrelated to
Baddeley's definition). Some systems may propose persistent storages that allow
the robot knowledge to grow over time, while other may offer a larger range of
memory categories, like short term memory (that lasts for a couple of seconds)
or episodic memory (that allows the robot to selectively remember facts
associated to specific events).

@@

        \item universal, existantial and cardinality constraints (including \concept{allValue}, 
        \concept{someValue}, \concept{hasValue}),

@@

As mentionned earlier, knowledge models based on description logics can be extended through rule languages.

@@

A monotonic system does not theoretically allow for knowledge retractation,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.
\fxfatal{Rephrase to emphasize that when new evidences appear, it is anyway often a
good idea to restart the reasoner.}

@@

\subsubsection{Presupposition Accommodation}
\label{sect|presupposition-accomodation}

@@

A knowledge representation system able to copte with presupposition
accommodation would be able to take into account this (usually under-defined)
information that is not grounded into perception for later inferences.

@@

As embodied entities, robots have to interact with physical entities.
\emph{Naive physics reasoning} covers all the everyday reasoning the humans
unconsciouly perform, like taking into account gravity (``if I drop a ball, it
falls down'') or common physical properties of objects (``a glass may break if
dropped'', etc.). Many of the interactions with our everyday environments are
ruled by such laws that are difficult to exhaustively encode.

@@

Knowledge acquision is generally not done directly in the knowledge
representation system. On the contrary, several, if not numerous, external
components are usually required to convert percepts into symbolic facts and to
ground them.

@@

In particular, complex robotic systems often require multi-modal perception
capabilities (for instance, a robot can only interpret an utterance like ``this
is a plate'' if it is able to understand gestures, understand natural language
and merge them in a timely manner). Multi-modal interpretation can take place
at various levels, but in many cases (especially if the modalities are of very
different natures, like in the example above) merging will require
symbolic-level reasoning. The KRS has a direct impact on the feasability and
ease of such operations.

@@

\emph{Grounding} (also called \emph{anchoring} when specifically refering to
building links between \emph{percepts} and \emph{physical
objects}~\cite{Coradeschi2003}) is the task consisting in building and
maintaining a bi-directional link between sub-symbolic representations (sensors
data, low-level actuation) and symbolic represtentations that can be
manipulated and reasoned about~\cite{Harnad1990}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Knowledge instanciation}

@@

Table \ref{table|surveyed-systems} presents the fifteen knowledge representation systems surveyed
in this article.

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
OMRKF & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
ARMAR/Tapas & KRS & Holzapfel, Waible \par (Karlsruhe TH) & & ? & TFS (Typed Feature Structures) & & \cite{Holzapfel2008}\\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
 & & Hertzberg (Osnabrück Univ.) \\
 (based on {\sc KnowRob} & & (JSK) \\
 OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\

@@

\end{tabular}
\end{center}
\caption{List of surveyed systems. Projects are listed by category (\emph{KRS} for systems that are explicit knowledge representation and reasoning modules, \emph{Ubiquitous} for systems where knowledge processing is fully distributed, \emph{Language} for languages used as KRS on robots), then names.}
\label{table|surveyed-systems}
\end{table}
\end{landscape}

@@

% More in details:
% - object identification based on viewpoint independent SIFT features
% - formalized anchoring system that explicitely match percieved attributes to predicates
% - Cyc predicates
% - ground 12 colors, based on a paper on color perception. Could be useful for us.
% - idem, they cite a paper on what spatial relations to compute
% - location of objects based on a previously provided semantic map (but not much on this semantic map)
% - two "memories": the robot memory stores the current list of percieved objects ; the archive memory stores what is not percieved anymore
% - uses directly Cyc (ie, 250 000 common sense concepts...), via CycL language -> 2nd and higher order logics (quantification over predicates, functions, etc)
% Remark: using 2nd order logic (ie meta statements), it would be easy to store the knowledge of each agent
% - disambiguation in concept name by asking human to decide amongst all concepts known by Cyc
% - template based natural language
% - experiment conducted in a "smart" indoor environmement + simple robot

@@

The PEIS framework offers through the \emph{PEIS middleware} a practical way to
insert a new component into the shared \emph{tuple space}.  Thus, the KR\&R
module can be seemlessly integrated into the PEIS ecosystem.

@@

\emph{NKRL} stands for \emph{Narrative Knowledge Representation Language}.
While this language is developped since a long time by Zarri~\cite{Zarri1997,
Zarri2008}, recent research direction include application to the robotic
field~\cite{Sabri2011}. NKRL is not {\it per-se} a knowledge representation
system, as it is primarily a language. However, it is used as the
representation and reasoning mechanism for robots by Sabri et al.

@@

CAS (\emph{CoSy Architecture Schema}) Toolkit~\cite{Hawes2007} is a
comprehensive toolkit aimed at builduing cognitive architectures for robots
through a set of interconnected SAs (\emph{subarchitectures}). The CAS does not
expose a central knowledge base as seen in previous works. It instead
represents knowledge as unrooted \emph{proxies}. Thoses proxies are formally
defined in \cite{Jacobsson2008} as $p= \langle F_p, u_p \rangle$ where $F_p$ is
a set of instanciated features (like $\phi^{Colour}_{red}$) and $u_p$ a
\emph{proxies union} that form an equivalence class corresponding to one
entity.

A union of proxies forms a global amodal representation of an entity, that can
be explicitely shared and manipulated. Being not centralized, the knowledge
model can be qualified of \emph{ubiquitous}. Futhermore, knowledge source in
the CAS architecture is tightly bound to the on-line grounding process (be it
grounded in perception or in dialogue). While nothing seems to prevent it, no
{\it a priori} knowledge (including common-sense knowledge) is used.

@@

GSM (for \emph{Grounded Situation Model})~\cite{Mavridis2006} is a knowledge
representation system primarly built to ``facilitate cross-modal
interoperability'',  especially in the context of verbal interaction with a
robot.

Unlike most of the previously presented systems, GSM does not rely on any
formal language but rather on a layered datastructure (Figure~\ref{fig|gsm})
that organizes the surrounding world into agents and relations between agents.
Each agent (any animate or inanimate object) is attached to a physical model (made
of \emph{body parts} that have properties like their position, color, etc.) and
a mental model (which is a recursively embedded GSM, thus allowing a sort of
theory of mind).

@@

    \caption{Simplified hierachical structure of the Grounded Situation Model,
    based on~\cite{Mavridis2006}}

@@

Properties are represented in three layers: a stochastic representation, close
to sensory percepts, a \emph{continous single-valued} encoding of the
stochastic model, and a discrete, categorical model.

@@

The Ontology-based Multi-layered Robot Knowledge Framework~\cite{Suh2007}
(OMKRF) is a knowledge representation system based on four inter-related
\emph{classes} of knowledge (Figure~\ref{fig|omrkf}). It proposes a layered
approach to knowledge representation that allows to integrate the grounding
process to the knowledge representation process. OMRKF knowledge model is
implemented with Horn clauses.

@@

Each level of knowledge is build as three stages of ontological realization: a
\emph{meta-concept} (the level itself, like ``temporal context'', ``behaviour''
or ``object feature'', a taxonomy of concepts inside this level (for instance
$cup : Object \sqsubseteq tableware : Object$) and an instanciation of the
taxonomy ($cup1 : cup$).

@@

Finally, the $Activity$ knowledge class store coumpound actions in a HTN-like
structure, exploited at run-time by a planner.

@@

\paragraph{Experiments} The Ke Jia robot has been demonstrated in several tasks
involving human-robot interaction with natural language. These tasks include a
task with multiple \emph{pick \& carry} that are globally optimized, naive
physics reasoning via teached rules or more complex scenarii with the robot
delivering drinks, taking into account changing and mutually exclusive
preferences of users.

@@

Another focus is put on handling unknown words and objects. {\sc Tapas}
provides routines to recognize unknown entities, and propose and interactive
and iterative verbal process to categorize (including adding new caterogies)
those new concepts.

@@

\begin{tabular}{lp{4cm}}
\toprule
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\midrule
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
NKLR &  None \\
CAST Proxies &  None \\
GSM &  Predefined categories \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
Ke Jia & None \\
ARMAR/{\sc Tapas} & Custom ontology related to the kitchen\\
Vincze & \\
(JSK) & \\

>>>>

Those questions have in common one prerequisite to be answered: the robot must
be able to manipulate \emph{explicitly} knowledge, and hence, need a way to
represent the knowledge.

@@

We have classified the features of knowledge representation systems (KRS) into
six broad categories: \emph{what can be represented?} or the
\emph{expressiveness} question ; \emph{how things are represented?} ; \emph{what
reasoning techniques are offered?} ; \emph{how knowledge is acquired and
anchored?} ; \emph{how the knowledge is made available and used by the other
components of the robot?} and \emph{which actual knowledge is stored?} or the
\emph{knowledge instantiation} question.

We have identified over ten projects that are either explicitly advertised as
knowledge representation systems or involve explicit knowledge manipulation
within a robot. By knowledge manipulation, we mean symbolic representation of
assertions, be it static statements on the world or spatio-temporal events, and
reasoning on this representation. Prominent features of each of these systems
illustrate how the various features of a knowledge representation system are
currently implemented.

@@

Every robotic system has, implicitly or not, some knowledge representation
systems. It may range from a simple state vector to an explicit symbolic
knowledge base.  This survey focuses on the right end of this spectrum:
symbolic systems, suited for abstract reasoning.

@@

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarily designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are able of on-line, dynamic knowledge acquisition and reasoning 
    (\ie not a simple static database).
\end{inparaenum}

@@

While classical cognitive architectures like {\sc Soar} or {\sc ACT-R} have
declarative knowledge modules~\cite{Derbinsky2010} and have been recently used
on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for instance), they are
also absent from this survey because we did not find much references in the
literature on knowledge manipulation and representation applied to robotic
scenarii in these architectures.

@@

In a slightly broader context, Heintz et al.~\cite{Heintz2008} define
\emph{knowledge processing middlewares} as systems supporting ``declarative
specifications for flexible configuration and dynamic reconfiguration of
context dependent processing at many different levels of abstraction''. They
identify six characteristics: the system must be able to merge informations
from different, possibly distributed sources; it should support quantitative as
well as qualitative processing of information, it should offer bottom-up and
top-down processing, it should be able to deal with uncertainty, allow for
``flexible configuration and reconfiguration'' (which require what we call
\emph{non-monotonicity} in this article) and eventually Heintz et al. call for
meta-knowledge and introspective capacities (``declarative specification of the
processing functionalities''). In this paper, we focus our analysis on similar
system with however an emphasize on the symbolic capabilities.

Several surveys compare global cognitive architectures (\cite{Vernon2007, Chong2009}).
Vernon et al.~\cite{Vernon2007} split these architectures into two broad
categories: the \emph{cognitivist} ones (where cognition is considered as an
explicit computation problem, often based on symbol manipulation), and the
\emph{emergent} ones (where cognition only exists as a result of the
interaction of the system with its environment). The approaches presented in
this paper are, at a few exceptions, prototypical \emph{cognitivist} approaches
that aim at making knowledge explicit within the robot architecture. Vernon et
al. propose twelve \emph{characteristics of cognitive system} to compare
architectures. Amongst them, they mention the \emph{inter-agent epistemology} (how
the structure of the world is captured in a representation and shared), the
relation to \emph{embodiment}, the ability to \emph{anticipate} and to
\emph{adapt}, and the mechanisms of \emph{motivation}. While presented at the
level of the whole robotic architecture, these features also translate into
knowledge representation strategies and are relevant to our study.

@@

Section~\ref{sect|surveyed-systems} then presents each of the systems we
examined, and underlines their specificities.

@@

A related ability is called \emph{pre-supposition accommodation}: if one of the
agent moves behind another one, with the brownie dough in its arm, and says
``be careful, I'm behind you!'', we want the first agent to be able to
represent both symbolically and geometrically (because, for instance, if the
agent want to move, it must take into account the new obstacle) something that
was not directly perceived. A knowledge representation system may be able to
provide structures to represent and reason about such cases.

@@

Note that most of these logic formalisms are still active research field by
their own, and practical considerations (especially the availability of
reasoners efficient enough for on-line use on a robot) often constraint the
choice of a logical formalism and a level of expressive power.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{expressive_overlap_dl_horn.pdf}
    \caption{expressiveness overlap of Description Logics and logic programs
    based on Horn clauses, taken from~\cite{Grosof2003}}
    \label{fig|overlap_dl_horn}
\end{figure}

Figure~\ref{fig|overlap_dl_horn} shows that the expressive power of description
logics and Horn clauses partially overlaps. In section~\ref{sect|reasoning} we
mention extensions to description logics based on rule systems to bring closer
the two approaches.

The relationships between expressive power and reasoning complexity that follow
has been extensively studied for Description Logics.
Zolin~\cite{ZolinDLComplexityNavigator} maintains a ``complexity navigator''
that allows to conveniently explore these relationships and indexes most of the
literature on that subject.

@@

Introspection must be distinguished from meta-cognition: While introspection
may require meta-cognition (for instance to be able to expose its internal
knowledge), it is not always mandatory. The current state of the robot can be
represented as a simple instantiation of a specific category (for instance, if
the robot give an object to the human, this state could be represented with the
triplets \setstmt{robot performs action1, action1 isA Give}.

@@

A particularly important aspect of introspection relates to the description of
its own capabilities: which sensors/actuators/computation services exist and
are currently available ?  While at a first level, these descriptions can be
static (\eg the robot has one laser scanner and two arms), at a second level,
the description is updated and reflect the current (and possibly past and
future) state of the robot. Note that these description may also involve
geometric descriptions (a kinematic chain, the pose of a device, etc.) that may
be deported outside of the main knowledge base. Efforts trying to formalize,
maintain and expose the capabilities and state of a robot are not new (and
ground themselves in work and techniques for self-descriptive remote procedure
calls in computing science), but take a renewed importance with applications
for high-level multi-robot cooperation. Recent work in that direction
include~\cite{Kunze2011}.

@@

Memory has been studied at length in the cognitive psychology and
neuropsychology communities: Atkinson and Shiffrin~\cite{Atkinson1968}
introduce the idea of \emph{short-term} and \emph{long-term} memory,
Anderson~\cite{Anderson1976} splits memory into \emph{declarative} (explicit)
and \emph{procedural} (implicit) memories, Tulving~\cite{Tulving1985} organizes
the concepts of \emph{procedural}, \emph{semantic} and \emph{episodic} memories
into a hierarchy. Short-term memory is refined with the concept of
\emph{working memory} by Baddeley~\cite{Baddeley2010}
(Figure~\ref{fig|memory_models}).

@@

Most knowledge representation systems offers some kind of memory as a pool of
facts that are not forgotten by the robot until it is halted (this memory is
often referred as a \emph{working memory}, but with a meaning unrelated to
Baddeley's definition). Some systems may propose persistent storages that allow
the robot knowledge to grow over time, while other may offer a larger range of
memory categories, like short term memory (that lasts for a couple of seconds)
or episodic memory (that allows the robot to selectively remember facts
associated to specific events).

@@

        \item universal, existential and cardinality constraints (including \concept{allValue}, 
        \concept{someValue}, \concept{hasValue}),

@@

As mentioned earlier, knowledge models based on description logics can be extended through rule languages.

@@

A monotonic system does not theoretically allow for knowledge retraction,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.
\fxfatal{Rephrase to emphasize that when new evidences appear, it is anyway often a
good idea to restart the reasoner.}

@@

\subsubsection{Presupposition Accommodation}
\label{sect|presupposition-accommodation}

@@

A knowledge representation system able to cope with presupposition
accommodation would be able to take into account this (usually under-defined)
information that is not grounded into perception for later inferences.

@@

As embodied entities, robots have to interact with physical entities.
\emph{Naive physics reasoning} covers all the everyday reasoning the humans
unconsciously perform, like taking into account gravity (``if I drop a ball, it
falls down'') or common physical properties of objects (``a glass may break if
dropped'', etc.). Many of the interactions with our everyday environments are
ruled by such laws that are difficult to exhaustively encode.

@@

Knowledge acquisition is generally not done directly in the knowledge
representation system. On the contrary, several, if not numerous, external
components are usually required to convert percepts into symbolic facts and to
ground them.

@@

In particular, complex robotic systems often require multi-modal perception
capabilities (for instance, a robot can only interpret an utterance like ``this
is a plate'' if it is able to understand gestures, understand natural language
and merge them in a timely manner). Multi-modal interpretation can take place
at various levels, but in many cases (especially if the modalities are of very
different natures, like in the example above) merging will require
symbolic-level reasoning. The KRS has a direct impact on the feasibility and
ease of such operations.

@@

\emph{Grounding} (also called \emph{anchoring} when specifically referring to
building links between \emph{percepts} and \emph{physical
objects}~\cite{Coradeschi2003}) is the task consisting in building and
maintaining a bi-directional link between sub-symbolic representations (sensors
data, low-level actuation) and symbolic representations that can be
manipulated and reasoned about~\cite{Harnad1990}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Knowledge instantiation}

@@

Table \ref{table|surveyed-systems} presents the eight knowledge representation
systems surveyed in this article.

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
OMRKF & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
ARMAR/Tapas & KRS & Holzapfel, Waible \par (Karlsruhe TH) & & ? & TFS (Typed Feature Structures) & & \cite{Holzapfel2008}\\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\end{tabular}
\end{center}

\caption{List of surveyed systems. Projects are listed by category (\emph{KRS}
for systems that are explicit knowledge representation and reasoning modules,
\emph{Ubiquitous} for systems where knowledge processing is fully distributed,
\emph{Language} for languages used as KRS on robots), then names.}

\label{table|surveyed-systems}
\end{table}
\end{landscape}

@@

% More in details:
% - object identification based on viewpoint independent SIFT features
% - formalized anchoring system that explicitly match percieved attributes to predicates
% - Cyc predicates
% - ground 12 colors, based on a paper on color perception. Could be useful for us.
% - idem, they cite a paper on what spatial relations to compute
% - location of objects based on a previously provided semantic map (but not much on this semantic map)
% - two "memories": the robot memory stores the current list of percieved objects ; the archive memory stores what is not percieved anymore
% - uses directly Cyc (ie, 250 000 common sense concepts...), via CycL language -> 2nd and higher order logics (quantification over predicates, functions, etc)
% Remark: using 2nd order logic (ie meta statements), it would be easy to store the knowledge of each agent
% - disambiguation in concept name by asking human to decide amongst all concepts known by Cyc
% - template based natural language
% - experiment conducted in a "smart" indoor environmement + simple robot

@@

The PEIS framework offers through the \emph{PEIS middleware} a practical way to
insert a new component into the shared \emph{tuple space}.  Thus, the KR\&R
module can be seamlessly integrated into the PEIS ecosystem.

@@

\emph{NKRL} stands for \emph{Narrative Knowledge Representation Language}.
While this language is developed since a long time by Zarri~\cite{Zarri1997,
Zarri2008}, recent research direction include application to the robotic
field~\cite{Sabri2011}. NKRL is not {\it per-se} a knowledge representation
system, as it is primarily a language. However, it is used as the
representation and reasoning mechanism for robots by Sabri et al.

@@

CAS (\emph{CoSy Architecture Schema}) Toolkit~\cite{Hawes2007} is a
comprehensive toolkit aimed at building cognitive architectures for robots
through a set of interconnected SAs (\emph{subarchitectures}). The CAS does not
expose a central knowledge base as seen in previous works. It instead
represents knowledge as unrooted \emph{proxies}. Those proxies are formally
defined in \cite{Jacobsson2008} as $p= \langle F_p, u_p \rangle$ where $F_p$ is
a set of instantiated features (like $\phi^{Colour}_{red}$) and $u_p$ a
\emph{proxies union} that form an equivalence class corresponding to one
entity.

A union of proxies forms a global amodal representation of an entity, that can
be explicitly shared and manipulated. Being not centralized, the knowledge
model can be qualified of \emph{ubiquitous}. Furthermore, knowledge source in
the CAS architecture is tightly bound to the on-line grounding process (be it
grounded in perception or in dialogue). While nothing seems to prevent it, no
{\it a priori} knowledge (including common-sense knowledge) is used.

@@

GSM (for \emph{Grounded Situation Model})~\cite{Mavridis2006} is a knowledge
representation system primarily built to ``facilitate cross-modal
interoperability'',  especially in the context of verbal interaction with a
robot.

Unlike most of the previously presented systems, GSM does not rely on any
formal language but rather on a layered data structure (Figure~\ref{fig|gsm})
that organizes the surrounding world into agents and relations between agents.
Each agent (any animate or inanimate object) is attached to a physical model (made
of \emph{body parts} that have properties like their position, color, etc.) and
a mental model (which is a recursively embedded GSM, thus allowing a sort of
theory of mind).

@@

    \caption{Simplified hierarchical structure of the Grounded Situation Model,
    based on~\cite{Mavridis2006}}

@@

Properties are represented in three layers: a stochastic representation, close
to sensory percepts, a \emph{continuous single-valued} encoding of the
stochastic model, and a discrete, categorical model.

@@

The Ontology-based Multi-layered Robot Knowledge Framework~\cite{Suh2007}
(OMRKF) is a knowledge representation system based on four inter-related
\emph{classes} of knowledge (Figure~\ref{fig|omrkf}). It proposes a layered
approach to knowledge representation that allows to integrate the grounding
process to the knowledge representation process. OMRKF knowledge model is
implemented with Horn clauses.

@@

Each level of knowledge is build as three stages of ontological realization: a
\emph{meta-concept} (the level itself, like ``temporal context'', ``behaviour''
or ``object feature'', a taxonomy of concepts inside this level (for instance
$cup : Object \sqsubseteq tableware : Object$) and an instantiation of the
taxonomy ($cup1 : cup$).

@@

Finally, the $Activity$ knowledge class store compound actions in a HTN-like
structure, exploited at run-time by a planner.

@@

\paragraph{Experiments} The Ke Jia robot has been demonstrated in several tasks
involving human-robot interaction with natural language. These tasks include a
task with multiple \emph{pick \& carry} that are globally optimized, naive
physics reasoning via taught rules or more complex scenarii with the robot
delivering drinks, taking into account changing and mutually exclusive
preferences of users.

@@

Another focus is put on handling unknown words and objects. {\sc Tapas}
provides routines to recognize unknown entities, and propose and interactive
and iterative verbal process to categorize (including adding new categories)
those new concepts.

@@

\begin{tabular}{lp{4cm}}
\toprule
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\midrule
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
NKLR &  None \\
CAST Proxies &  None \\
GSM &  Predefined categories \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
Ke Jia & None \\
ARMAR/{\sc Tapas} & Custom ontology related to the kitchen\\
